\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-16 lang-design.tex
stlc compilation figure

\begin{centered}
\begin{minipage}{.71\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_rec : \forall (P : tm -> Set), [@\hlcase{tm-recursor-case-var}@](\forall x, P (tm_var x))[@\tikzmarkend{tm-recursor-case-var}@] -> [@\hlcase{tm-recursor-case-unit}@]P tm_unit[@\tikzmarkend{tm-recursor-case-unit}@] ->
         [@\hlcase{tm-recursor-case-abs}@](\forall x t, P t -> P (tm_abs x t))[@\tikzmarkend{tm-recursor-case-abs}@] ->
         [@\hlcase{tm-recursor-case-app}@](\forall t1, P t1 -> \forall t2, P t2 -> P (tm_app t1 t2))[@\tikzmarkend{tm-recursor-case-app}@] -> \forall t, P t
\end{lstlisting}
\end{minipage}
\end{centered}

@@

With inductive types made extensible, exhaustivity of induction becomes
in jeopardy, however.
In particular, recursor "tm_rec" should no longer be allowed, because
its type mentions "tm", whose meaning is late bound, yet
"tm_rec" purports to claim \lsti{\forall t, P t} given only four case handlers.

@@

Coq provides tactics for proving injectivity and disjointness of constructors
(i.e., \lsti{injection} and \lsti{discriminate}).
The proof terms generated by the tactics involve exhaustively
matching on the constructors of an inductive type, so
they do not work for extensible inductive types (\ref{chg:extensible-v-exhaustive}).
%
In principle, the programmer could use \lsti{FInduction} to prove
injectivity and disjointness.
But this workaround is unsatisfying:
it is tedious, it forces the programmer to revisit
the induction proofs every time an inductive type is extended,
and above all, why should a property like
\lsti{tm_var "x" = tm_abs "y" t -> False} have anything to do with "tm_fix"?

@@

As analyzed earlier, ordinary recursors, such as "tm_rec", are impossible
within a family in which the name of the inductive type is late bound.
However,
a key observation is that extensible inductive types still admit a
weakened elimination principle where the motive is an \lsti{option} type.
For example, within family "STLC", the partial recursor for
"tm" has the following type:

\begin{centered}
\begin{minipage}{.96\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_prec_STLC : \forall (P : tm -> Set), [@\hlcase{tm-partialrec-case-var}@](\forall x, option (P (tm_var x)))[@\tikzmarkend{tm-partialrec-case-var}@] -> [@\hlcase{tm-partialrec-case-unit}@]option (P tm_unit)[@\tikzmarkend{tm-partialrec-case-unit}@] ->
               [@\hlcase{tm-partialrec-case-abs}@](\forall x t, option (P t) -> option (P (tm_abs x t)))[@\tikzmarkend{tm-partialrec-case-abs}@] ->
               [@\hlcase{tm-partialrec-case-app}@](\forall t1, option (P t1) -> \forall t2, option (P t2) -> option (P (tm_app t1 t2)))[@\tikzmarkend{tm-partialrec-case-app}@] ->
               \forall t, option (P t)
\end{lstlisting}
\end{minipage}
\end{centered}

\noindent
As expected, "tm_prec_STLC" is axiomatized along with
four (propositional) equalities, one for each constructor of "tm".
For instance, the equality for constructor "tm_abs" is as follows:

\begin{centered}
\begin{minipage}{.99\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_abs_eq_STLC: \forall x t P H1 H2 H3 H4,
                tm_prec_STLC P H1 H2 H3 H4 (tm_abs x t) = H3 x t (tm_prec_STLC P H1 H2 H3 H4 t)
\end{lstlisting}
\end{minipage}
\end{centered}

%\noindent
Importantly, unlike the standard "tm_rec" recursor, the partial recursor
"tm_prec_STLC" is compatible with the late binding of "tm" in its type.
When "tm_prec_STLC" is inherited into family "STLCFix", all the previous four equalities
still hold, and a trivial, fifth equality is made available:

\begin{centered}
\begin{minipage}{.88\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_fix_eq_STLC : \forall x t P H1 H2 H3 H4, tm_prec_STLC P H1 H2 H3 H4 (tm_fix x t) = None
\end{lstlisting}
\end{minipage}
\end{centered}

@@

\begin{centered}
\begin{minipage}{.96\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_prec_STLC (\lambda[@\,@]_, \nat) (\lambda[@\,@]_, Some 1) (Some 2) (\lambda[@\,@]_[@\,@]_[@\,@]_, Some 3) (\lambda[@\,@]_[@\,@]_[@\,@]_[@\,@]_, Some 4) (tm_var "x") =
tm_prec_STLC (\lambda[@\,@]_, \nat) (\lambda[@\,@]_, Some 1) (Some 2) (\lambda[@\,@]_[@\,@]_[@\,@]_, Some 3) (\lambda[@\,@]_[@\,@]_[@\,@]_[@\,@]_, Some 4) (tm_abs "y" t)
\end{lstlisting}
\end{minipage}
\end{centered}

\noindent
and then rewrites the above equality using two of the axiomatized
equalities about "tm_prec_STLC",
%(namely "tm_var_eq_STLC" and "tm_abs_eq_STLC"),
obtaining \lsti{Some 1 = Some 4},
from which \lsti{False} easily follows.

Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
equalities are compatible with the late binding of "tm".
Also note that within family "STLCFix", a second partial recursor
(called "tm_prec_STLCFix") and its equalities are available,
allowing properties about "tm_fix",
such as \lsti{\neg(tm_var "x" = tm_fix "y" t)}, to be proved.

>>>>

\begin{centered}
\begin{minipage}{.71\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_rect : \forall (P : tm -> Type), [@\hlcase{tm-recursor-case-unit}@]P tm_unit[@\tikzmarkend{tm-recursor-case-unit}@] -> [@\hlcase{tm-recursor-case-var}@](\forall x, P (tm_var x))[@\tikzmarkend{tm-recursor-case-var}@] ->
         [@\hlcase{tm-recursor-case-abs}@](\forall x t, P t -> P (tm_abs x t))[@\tikzmarkend{tm-recursor-case-abs}@] ->
         [@\hlcase{tm-recursor-case-app}@](\forall t1, P t1 -> \forall t2, P t2 -> P (tm_app t1 t2))[@\tikzmarkend{tm-recursor-case-app}@] -> \forall t, P t
\end{lstlisting}
\end{minipage}
\end{centered}

@@

With inductive types made extensible, exhaustivity of induction becomes
in jeopardy, however.
In particular, recursor "tm_rect" should no longer be allowed, because
its type mentions "tm", whose meaning is late bound, yet
"tm_rect" purports to claim \lsti{\forall t, P t} given only four case handlers.

@@

Coq provides tactics for proving injectivity and disjointness of constructors
(i.e., \lsti{injection} and \lsti{discriminate}).
The proof terms generated by the tactics involve exhaustively
matching on the constructors of an inductive type, so
they do not work for extensible inductive types (\ref{chg:extensible-v-exhaustive}).
%
In principle, the programmer could use \lsti{FInduction} to prove
injectivity and disjointness.
But this workaround is unsatisfying:
it is tedious, it forces the programmer to revisit
the induction proofs every time an inductive type is extended,
and above all, why should a property like
\lsti{\neg(tm_var "x" = tm_abs "y" t)} have anything to do with "tm_fix"?

@@

As analyzed earlier, ordinary recursors, such as "tm_rect", are impossible
within a family in which the name of the inductive type is late bound.
However,
a key observation is that extensible inductive types still admit a
weakened elimination principle where the motive is an \lsti{option} type.
For example, within family "STLC", the partial recursor for
"tm" has the following type:

\begin{centered}
\begin{minipage}{.97\textwidth}
\newcommand\hlcase[1]{\tikzmarkin[disable rounded corners=true,set fill color=yellow!18,set border color=yellow!18]{#1}(0.00,-0.05)(-0.00,0.20)}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_prect_STLC : \forall (P : tm -> Type), [@\hlcase{tm-partialrec-case-unit}@]option (P tm_unit)[@\tikzmarkend{tm-partialrec-case-unit}@] -> [@\hlcase{tm-partialrec-case-var}@](\forall x, option (P (tm_var x)))[@\tikzmarkend{tm-partialrec-case-var}@] ->
                [@\hlcase{tm-partialrec-case-abs}@](\forall x t, option (P t) -> option (P (tm_abs x t)))[@\tikzmarkend{tm-partialrec-case-abs}@] ->
                [@\hlcase{tm-partialrec-case-app}@](\forall t1, option (P t1) -> \forall t2, option (P t2) -> option (P (tm_app t1 t2)))[@\tikzmarkend{tm-partialrec-case-app}@] ->
                \forall t, option (P t)
\end{lstlisting}
\end{minipage}
\end{centered}

\noindent
As expected, "tm_prect_STLC" is axiomatized along with
four (propositional) equalities, one for each constructor of "tm".
For instance, the equality for constructor "tm_abs" is as follows:

\begin{centered}
\begin{minipage}{\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_abs_eq_STLC: \forall x t P H1 H2 H3 H4,
                tm_prect_STLC P H1 H2 H3 H4 (tm_abs x t) = H3 x t (tm_prect_STLC P H1 H2 H3 H4 t)
\end{lstlisting}
\end{minipage}
\end{centered}

%\noindent
Importantly, unlike the standard "tm_rect" recursor, the partial recursor
"tm_prect_STLC" is compatible with the late binding of "tm" in its type.
When "tm_prect_STLC" is inherited into family "STLCFix", all the previous four equalities
still hold, and a trivial, fifth equality is made available:

\begin{centered}
\begin{minipage}{.88\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_fix_eq_STLC : \forall x t P H1 H2 H3 H4, tm_prect_STLC P H1 H2 H3 H4 (tm_fix x t) = None
\end{lstlisting}
\end{minipage}
\end{centered}

@@

\begin{centered}
\begin{minipage}{.98\textwidth}
\begin{lstlisting}[basicstyle=\fontsize{8.25}{9}\ttfamily]
tm_prect_STLC (\lambda[@\,@]_, \nat) (\lambda[@\,@]_, Some 1) (Some 2) (\lambda[@\,@]_[@\,@]_[@\,@]_, Some 3) (\lambda[@\,@]_[@\,@]_[@\,@]_[@\,@]_, Some 4) (tm_var "x") =
tm_prect_STLC (\lambda[@\,@]_, \nat) (\lambda[@\,@]_, Some 1) (Some 2) (\lambda[@\,@]_[@\,@]_[@\,@]_, Some 3) (\lambda[@\,@]_[@\,@]_[@\,@]_[@\,@]_, Some 4) (tm_abs "y" t)
\end{lstlisting}
\end{minipage}
\end{centered}

\noindent
and then rewrites the above equality using two of the axiomatized
equalities about "tm_prect_STLC",
%(namely "tm_var_eq_STLC" and "tm_abs_eq_STLC"),
obtaining \lsti{Some 1 = Some 4},
from which \lsti{False} easily follows.

Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
equalities are compatible with the late binding of "tm".
Also note that within family "STLCFix", a second partial recursor
(called "tm_prect_STLCFix") and its equalities are available,
allowing properties about "tm_fix",
such as \lsti{\neg(tm_var "x" = tm_fix "y" t)}, to be proved.

### 2022-10-16 stlc-compiled.tex
stlc compilation figure

\lstset{
  basicstyle=\fontsize{8}{8.5}\ttfamily,
% numbers=left,
}

@@

\newcommand{\innersep}{\vspace{5pt}}

\begin{lstlisting}
Module Type STLC\_ty\_Ctx.[@\tanc{c-STLC-ty-start}@]
End STLC\_ty\_Ctx.[@\innersep@]
Module Type STLC\_ty (self : STLC\_ty\_Ctx).
Parameter ty : Set.
Parameter ty_unit : ty.
Parameter ty_arrow : ty -> ty -> ty.
Parameter ty_prec_STLC : [@\dadada@].[@\hfill\codecomment{partial recursor}@]
Parameter ty_unit_eq_STLC : [@\dadada@].[@\hfill\codecomment{eq.\ on recursor}@]
Parameter ty_arrow_eq_STLC : [@\dadada@].[@\codecomment{eq.\ on recursor}@]
End STLC\_ty.[@\tanc{c-STLC-ty-end}@]

Module Type STLC\_tm\_Ctx.[@\tanc{c-STLC-tm-start}@]
Include STLC\_ty\_Ctx.  Include STLC\_ty.
End STLC\_tm\_Ctx.[@\innersep@]
Module Type STLC\_tm (self : STLC\_tm\_Ctx).
Parameter tm : Set.
[@\dadada@][@\hfill\codecommentstart{axiomatized \texttt{tm} constructors, partial recursor}@]
[@\hfill\codecommentend{\texttt{tm\_prec\_STLC}, and its four equalities}@]
End STLC\_tm.[@\tanc{c-STLC-tm-end}@]

Module Type STLC\_env\_Ctx.[@\tanc{c-STLC-env-start}@]
Include STLC\_tm\_Ctx.  Include STLC\_tm.
End STLC\_env\_Ctx.[@\innersep@]
Module STLC\_env (self : STLC\_env\_Ctx).
Definition env : Type := id -> option self.ty.
End STLC\_env.[@\tanc{c-STLC-env-end}@]

Module Type STLC\_empty\_Ctx.[@\tanc{c-STLC-empty-start}@]
Include STLC\_env\_Ctx.  Include STLC\_env.
End STLC\_empty\_Ctx.[@\innersep@]
Module STLC\_empty (self : STLC\_empty\_Ctx).
Definition empty : self.env := \lambda _, None.
End STLC\_empty.[@\tanc{c-STLC-empty-end}@]

[@\dadada@][@\hfill\codecomment{compilation of \texttt{hasty}, \texttt{value}}@]

Module Type STLC\_subst\_Ctx.[@\tanc{c-STLC-subst-start}@]
Include STLC\_value\_Ctx.  Include STLC\_value.
End STLC\_subst\_Ctx.[@\innersep@]
Module STLC\_subst\_Cases (self : STLC\_subst\_Ctx).
Definition STLC\_subst\_tm_unit :=
  \lambda (x : id) (t : self.tm), self.tm_unit.
Definition STLC\_subst\_tm_var := [@\dadada@].
Definition STLC\_subst\_tm_abs := [@\dadada@].
Definition STLC\_subst\_tm_app := [@\dadada@].
End STLC\_subst\_Cases.[@\innersep@]
Module Type STLC\_subst (self : STLC\_subst\_Ctx).
Parameter subst : self.tm[@\,@]->[@\,@]id[@\,@]->[@\,@]self.tm[@\,@]->[@\,@]self.tm.
Parameter subst_tm_unit_eq : \forall x t,
  self.subst (self.tm_unit) x t = self.tm_unit.
Parameter subst_tm_var_eq : [@\dadada@].
Parameter subst_tm_abs_eq : [@\dadada@].
Parameter subst_tm_app_eq : [@\dadada@].
End STLC\_subst.[@\tanc{c-STLC-subst-end}@]

[@\dadada@][@\hfill\codecomment{compilation of rest of family \texttt{STLC}}@][@\columnbreak@]

[@~@]
\end{lstlisting}

\makeline[0pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!50]
\makeline[0pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!50]
\makeline[0pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!50]
\makeline[0pt]{c-STLC-empty-start}{c-STLC-empty-end}[codecomment-color!50]
\makeline[0pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!50]

\end{multicols}
\end{minipage}
\caption{Compilation of the STLC mechanizations in \cref{fig:stlc-mechanized} to parameterized Coq modules.}
\label{fig:stlc-compiled}
\end{figure}

>>>>

\lstset{
  basicstyle=\fontsize{8}{7.8}\ttfamily,
% numbers=left,
}

@@

\newcommand{\innersep}{\vspace{4pt}}
\newcommand{\outersep}{\vspace{4pt}}
\newcommand{\outdent}{\!\!\!}

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLC}}@][@\tanc{c-STLC-tm-start}@]
[@\outdent@]Module Type STLC\_tm\_Ctx.
[@\outdent@]End STLC\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLC\_tm (self : STLC\_tm\_Ctx).
Axiom tm : Set.
Axiom tm_unit : tm.[@\hfill@]Axiom tm_var : id -> tm.
Axiom tm_abs : id -> tm -> tm.
Axiom tm_app : tm -> tm -> tm.
Axiom tm_prect_STLC : [@\dadada@].
Axiom [@\textls[-30]{tm\_unit\_eq\_STLC}@][@\;:\;@][@\dadada@]. Axiom [@\textls[-30]{tm\_abs\_eq\_STLC}@][@\;:\;@][@\dadada@].
Axiom [@\textls[-30]{tm\_abs\_eq\_STLC}@][@\;:\;@][@\dadada@].  Axiom [@\textls[-30]{tm\_app\_eq\_STLC}@][@\;:\;@][@\dadada@].
[@\outdent@]End STLC\_tm.[@\tanc{c-STLC-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLC}}@][@\tanc{c-STLC-subst-start}@]
[@\outdent@]Module Type STLC\_subst\_Ctx.
Include STLC\_tm\_Ctx.  Include STLC\_tm.
[@\outdent@]End STLC\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLC\_subst\_Cases (self : STLC\_subst\_Ctx).
Def subst\_tm_unit :=
  \lambda (x : id) (t : self.tm), self.tm_unit.
Def subst\_tm_var := [@\dadada@].
Def subst\_tm_abs := [@\dadada@].  Def subst\_tm_app := [@\dadada@].
[@\outdent@]End STLC\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLC\_subst (self : STLC\_subst\_Ctx).
Axiom subst : self.tm[@\,@]->[@\,@]id[@\,@]->[@\,@]self.tm[@\,@]->[@\,@]self.tm.
Axiom subst_tm_unit_eq : \forall x t,
  self.subst (self.tm_unit) x t = self.tm_unit.
Axiom subst_tm_var_eq : [@\dadada@].
Axiom subst_tm_abs_eq : [@\dadada@].
Axiom subst_tm_app_eq : [@\dadada@].
[@\outdent@]End STLC\_subst.[@\tanc{c-STLC-subst-end}@][@\outersep@]
[@\outdent@][@\dadada@][@\hfill\codecomment{Code emitted upon definition of \texttt{ty} in family \texttt{STLC}}@][@\tanc{c-STLC-ty-start}@][@\tanc{c-STLC-ty-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{env} in family \texttt{STLC}}@][@\tanc{c-STLC-env-start}@]
[@\outdent@]Module Type STLC\_env\_Ctx.
Include STLC\_ty\_Ctx.  Include STLC\_ty.
[@\outdent@]End STLC\_env\_Ctx.[@\innersep@]
[@\outdent@]Module STLC\_env (self : STLC\_env\_Ctx).
Def env : Type := id -> option self.ty.
[@\outdent@]End STLC\_env.[@\tanc{c-STLC-env-end}@][@\outersep@]
[@\outdent@][@\dadada@][@\hfill\codecomment{Code emitted for other fields defined in family \texttt{STLC}}@][@\tanc{c-STLC-rest}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon completion of family \texttt{STLC}}@][@\tanc{c-STLC-start}@]
[@\outdent@]Module STLC.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLC-d-tm-start}@]
| tm_unit\_ : tm\_    | tm_var\_ : id -> tm\_
| tm_abs\_  : id -> tm\_ -> tm\_
| tm_app\_  : tm\_ -> tm\_ -> tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
[@\hfill\codecomment{Instantiate \texttt{tm} partial recursor \& equalities}@]
Def tm_prect_STLC P H1 H2 H3 H4 : \forall t, P t :=
  fix F t := match t with
  | tm_unit\_ => H1  | tm_var\_ x => H2 x
  | tm_abs\_ x t => H3 x t (F t)
  | tm_app\_ t1 t2 => H4 t1 (F t1) t2 (F t2) end.
Fact[@\;@][@\textls[-35]{tm\_unit\_eq\_STLC}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-tm-end}@][@\innersep@]
Include STLC\_subst\_Cases.[@\tanc{c-STLC-d-subst-start}@]
[@\hfill\codecomment{Instantiate \texttt{subst} \& equalities}@]
Def subst[@\,@]:[@\,@]tm[@\,@]->[@\,@]id[@\,@]->[@\,@]tm[@\,@]->[@\,@]tm :=[@\tanc{c-STLC-firstcol-end}\columnbreak@]
  tm\__rect _ subst\_tm_unit subst\_tm_var[@\tanc{c-STLC-sndcol-start}@]
             subst\_tm_abs  subst\_tm_app.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{ty}, its constructors, partial recusor \& eq.}@][@\tanc{c-STLC-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLC-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLC}}@][@\tanc{c-STLC-d-rest}@][@\innersep@]
[@\outdent@]End STLC.[@\tanc{c-STLC-end}@]
\end{lstlisting}

\makeline[0pt]{c-STLC-subst-start}{c-STLC-subst-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-tm-start}{c-STLC-tm-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-ty-start}{c-STLC-ty-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-env-start}{c-STLC-env-end}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-rest}{c-STLC-rest}[codecomment-color!50][1.25pt]
\makeline[0pt]{c-STLC-start}{c-STLC-firstcol-end}[codecomment-color!50][1.25pt]
\makeline[4pt]{c-STLC-d-tm-start}{c-STLC-d-tm-end}[codecomment-color!25][1.25pt]
\makeline[4pt]{c-STLC-d-subst-start}{c-STLC-firstcol-end}[codecomment-color!20][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLC-sndcol-start}{c-STLC-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-sndcol-start}{c-STLC-d-subst-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-ty}{c-STLC-d-ty}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-env}{c-STLC-d-env}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLC-d-rest}{c-STLC-d-rest}[codecomment-color!25][1.25pt]

\vspace{-15pt}

\colorlet{codecomment-color}{orange}

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@]STLCFix\_subst\_Ctx).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\dadada@] [@\codecomment{Code emitted for other fields defined in family \texttt{STLCFix}}@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon completion of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_ : tm\_    | tm_var\_ : id -> tm\_
| tm_abs\_  : id -> tm\_ -> tm\_
| tm_app\_  : tm\_ -> tm\_ -> tm\_
| tm_fix\_  : id -> tm\_ -> tm\_.
Def tm := tm\_.[@\hfill\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\dadada@][@\hfill\codecomment{Instantiate \texttt{tm} partial recursors \& equalities}@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\hfill\codecomment{Instantiate \texttt{subst} \& equalities}@]
Def subst[@\,@]:[@\,@]tm[@\,@]->[@\,@]id[@\,@]->[@\,@]tm[@\,@]->[@\,@]tm :=
  tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\dadada@][@\hfill\codecomment{Include/Instantiate other fields of family \texttt{STLCFix}}@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[.5\textwidth+9pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+9pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!50][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!25][1.25pt]
\makeline[.5\textwidth+13pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!25][1.25pt]

\vspace{-15pt}

\definecolor{codecomment-color}{HTML}{000080}

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon command \texttt{Check} \dadada}@][@\tanc{c-Check-STLCFix-typesafe-start}@]
[@\outdent@]Check STLCFix.typesafe.[@\tanc{c-Check-STLCFix-typesafe-end}@]
\end{lstlisting}

\makeline[.5\textwidth+9pt]{c-Check-STLCFix-typesafe-start}{c-Check-STLCFix-typesafe-end}[codecomment-color!35][1.25pt]

\end{multicols}
\end{minipage}

\vspace{-8pt}

\caption{Compilation of the mechanization of the STLCs in \cref{fig:stlc-mechanized} to parameterized Coq modules.}
\label{fig:stlc-compiled}
\end{figure}
